### 2022-12-01 README.Rmd
update to readme
Update readme

### Summary

@@

@@

Here is an example using a dataset from the `ppmData` package. We setup a quadrature scheme for the species \textit{Tasmaphena sinclairi} located within Tasmania, Australia.

@@

Here we plot the quadrature scheme. The red points represent the known locations of \textit{Tasmaphena sinclairi}. The black points represent the quadrature locations. Quasi-random quadrature where the integration points are generated using a quasi-random areal sample.
```{r fig1, fig.width=7, fig.height=4, fig.align='center', echo=TRUE}
plot(ppmdata1)
```
## Code of Conduct

@@

### References

>>>>

## Summary

@@

## Using the ppmData package

@@

Here is an example using a dataset from the `ppmData` package. We setup a quadrature scheme for the species *Tasmaphena sinclairi* located within Tasmania, Australia.

@@

Here we plot the quadrature scheme. The green points represent the known locations of *Tasmaphena sinclairi*. The black points represent the quadrature locations. Quasi-random quadrature where the integration points are generated using a quasi-random areal sample.

```{r fig1, fig.width=7, fig.height=4, fig.align='center', echo=TRUE}
plot(ppmdata1)
```
Once the `ppmData` object has been set up it is quiet easy to fit a point process model in R. You can use something like `glm`, `gam` or even convert the `ppmData` object to work directly with `spatstat::ppm`.

## Code of Conduct

@@

## References
